Supporting Information

### 2018-02-24 SupportingInformation.Rmd
minor tweak

# Aphid raw data for count
d0_count<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))

# Aphid raw data for first flight
d0_firstflight<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtsfirstflight141117.csv",header=F))

# Aphid raw data for flight duration
d0_flightduration<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtsflightduration141117.csv",header=F))

>>>>

# Aphid raw data for count
d0_count<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))

# Aphid raw data for first flight
d0_firstflight<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtsfirstflight141117.csv",header=F))

## Aphid raw data for flight duration
#d0_flightduration<-as.matrix(read.csv("Data/Aphid_data/APHID_DATA_RAW/aphidtsflightdu#ration141117.csv",header=F))
